Ice sheet mass flows

### 2024-07-05 sankey.tex
Horizontal flow and re-order outputs top-to-bottom

\begin{tikzpicture}[remember picture, overlay, shift={(5.5,-1.5)}]

@@

    \sankeyset{
      %% comment for gray outline
      draw/.style={
        draw=white,
        line width=0pt,line cap=round,line join=round,
      },
      every node/.style={angle=-90},
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/33,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      ice-to-water/.style={fill/.style={fill=none, top color=ice, bottom color=water},},
      ice-to-water-horiz/.style={fill/.style={fill=none, right color=ice, left color=water},},
      ice-to-air/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-air-horiz/.style={fill/.style={fill=none, left color=ice, right color=air},},
      water-to-air-horiz/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, top color=water, bottom color=air},},
      air-to-ice/.style={fill/.style={fill=none, top color=air, bottom color=ice},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      red-to-ice/.style={fill/.style={fill=none, top color=red, bottom color=ice},},
      water-to-ice/.style={fill/.style={fill=none, top color=water, bottom color=ice},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      black-to-ice/.style={fill/.style={fill=none, bottom color=ice, top color=black},},
      in-black/.style={draw/.style={draw=gray,thick=3},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\ttfamily,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

    \newcommand\abovelabel[1]{ % valname
      \node[font=\tiny, rotate=45, anchor=north west]
      at ([yshift=5mm,xshift=-3mm]#1.center) {\qq{#1}: \Lab{v#1}};
    }
    \newcommand\belowlabel[2]{ % valname
      \node[font=\tiny, rotate=45, anchor=north east]
      at ([yshift=-2mm,xshift=0mm]#1.center) {\Lab{#2}: \qq{#1}};
    }

@@

    \sankeyset{ice} % default color until otherwise specified
    \newcommand\xoff{2mm}

    \sankeynode{name=SF, quantity=\Q{vSF}}
    \sankeynode{name=DP, quantity=\Q{vDP}, at={[xshift=-\xoff]SF.right}, anchor=left}
    \sankeynode{name=CD, quantity=\Q{vCD}, at={[xshift=-\xoff]DP.right}, anchor=left}
    \sankeynode{name=RF, quantity=\Q{vRF}, at={[xshift=-\xoff]CD.right}, anchor=left}

    \abovelabel{SF}
    \abovelabel{DP}
    \abovelabel{CD}
    \abovelabel{RF}

@@

    \sankeynode{name=f0, quantity=\Q{vSF}+\Q{vDP}+\Q{vCD}+\Q{vRF},
      at={[yshift=-15mm]SF.left}, anchor=left,
      forked={\Q{vSF}/SFi, \Q{vDP}/DPi, \Q{vCD}/CDi, \Q{vRF}/RFi}}

@@

    \ifthenelse{\Q{vMG} > \Q{vML}} {
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vFRGAIN}/FG, \Q{vRFZ}/RFZi}}
    } {
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vML}/MLi, \Q{vFRGAIN}/FG, \Q{vRFZ}/RFZi}}
    }

@@

    \ifthenelse{\Q{vMG} > \Q{vML}}
    {
      \sankeyfork{f1}{
        \Q{vMG}/MG,
        \Q{vSU}/SU,
        \Q{vFRLOSS}/FL,
        \Q{vGZRET}/GZ,
        \Q{vDYN}/f6, \Q{vBM}/BM, \Q{vRU}+\Q{vEV}/f8, \Q{vRFZ}/RFZo}
    }
    {
      \sankeyfork{f1}{
        %% \Q{vMG}/MG,
        \Q{vSU}/SU,
        \Q{vFRLOSS}/FL,
        \Q{vGZRET}/GZ,
        \Q{vDYN}/f6, \Q{vBM}/BM, \Q{vRU}+\Q{vEV}/f8, \Q{vRFZ}/RFZo}
    }

    \sankeydubins[minimum radius=5mm,ice-to-water-horiz]{RFZo}{RFZi}

    \sankeyadvance{f6}{10mm}
    \sankeyfork{f6}{\Q{vICE}/D, \Q{vSUB}/SUB}
    \sankeyadvance{D}{10mm}

    \sankeynode{name=SUBa, quantity=\qq{SUB}, at={[xshift=-\xoff]D.right}, anchor=left}
    \sankeyoutin[ice-to-water]{SUB}{SUBa}

    \sankeynode{name=BMa, quantity=\qq{BM}, at={[xshift=-\xoff]SUBa.right}, anchor=left}
    \sankeyoutin[ice-to-water]{BM}{BMa}

    \sankeynode{name=f8a, quantity=\qq{f8}, at={[xshift=-\xoff]BMa.right}, anchor=left}
    \sankeyoutin[ice-to-water]{f8}{f8a}

    \sankeynode{name=GZa, quantity=\qq{GZ}, at={[xshift=\xoff]D.left}, anchor=right}
    \sankeyoutin{GZ}{GZa}

    \sankeynode{name=FLa, quantity=\qq{FL}, at={[xshift=\xoff]GZa.left}, anchor=right}
    \sankeyoutin{FL}{FLa}

    \sankeynode{name=SUa, quantity=\qq{SU}, at={[xshift=\xoff]FLa.left}, anchor=right}
    \sankeyoutin{SU}{SUa}

    \sankeyadvance[out-red]{FLa}{10mm}
    \sankeyend[out-red]{FLa}
    \belowlabel{FLa}{vFRLOSS}

    \ifnum \numexpr\Q{vMG} > \Q{vML}
      \sankeynode{name=MGa, quantity=\qq{MG},
        at={[xshift=3mm,yshift=-3mm]MG.left}, anchor=left, angle=0}
      \node[font=\tiny, anchor=north]
      at ([yshift=0mm,xshift=3mm]MGa.south) {\qq{MGa}: Mass gain};
      \sankeyoutin{MG}{MGa}
    \fi

    \sankeyfork{f8a}{\Q{vRU}/RU, \Q{vEV}/EV}
    \sankeynode{name=EVa, quantity=\qq{EV},
      at={[xshift=-3mm,yshift=-5mm]f8a.right}, anchor=right, angle=180}
    \sankeyoutin[water]{EV}{EVa}
    \sankeyadvance[water-to-air-horiz]{EVa}{5mm}
    \sankeyend[air]{EVa}

    \ifthenelse{\Q{vMG} < \Q{vML}} { % mass loss
      \sankeynode{name=ML, quantity=\Q{vML}, at={[xshift=-\xoff]RF.right}, anchor=left}
      \abovelabel{ML}

      % frontal advance next to drawdown (mass loss)
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[yshift=-5mm,xshift=-\xoff]ML.right}, anchor=left}

      \sankeystart[red]{ML}
      \sankeyadvance[red-to-ice]{ML}{5mm}
      \sankeyoutin{ML}{MLi}
    }{ % mass gain
      \sankeyadvance[ice-to-black]{MGa}{3mm}
      \sankeyend[black]{MGa}
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[yshift=15mm,xshift=3mm]RFZi.right}, anchor=left}
    }

    \ifnum \numexpr\qq{FGi} > 0
    \sankeystart[in-black]{FGi}
    \sankeyoutin[in-black]{FGi}{FG}
    \node[font=\tiny, rotate=45, anchor=north east]
    at ([yshift=12mm,xshift=3mm]FGi.right) {Frontal advance: \qq{FGi}};
    \fi

    \sankeynode{name=SUaa, quantity=\qq{SU},
      at={[xshift=2mm,yshift=-5mm]SUa.left}, anchor=left, angle=0}
    \sankeyoutin[ice]{SUa}{SUaa}
    \sankeyadvance[ice-to-air-horiz]{SUaa}{2mm}
    \sankeyend[air]{SUaa}

    \sankeyadvance[ice-to-water,out-red]{GZa}{10mm}
    \sankeyend[water,out-red]{GZa}
    \sankeyadvance{D}{10mm}
    \sankeyend{D}

    \sankeyset{water}
    \sankeyadvance{BMa}{10mm}; \sankeyend{BMa}
    \sankeyadvance{SUBa}{10mm}; \sankeyend{SUBa}
    \sankeyadvance{RU}{10mm}; \sankeyend{RU}

    \belowlabel{RU}{vRU}
    \belowlabel{BMa}{vBM}
    \belowlabel{SUBa}{vSUB}
    \belowlabel{D}{vICE}
    \belowlabel{GZa}{vGZRET}

    \node[font=\tiny, rotate=45, anchor=north east]
    at ([yshift=1mm,xshift=3mm]SUaa.south) {\Lab{vSU}: \qq{SUaa}};

    \node[font=\tiny, rotate=45, anchor=north east]
    at ([yshift=0mm,xshift=5mm]EVa.north) {\Lab{vEV}: \qq{EVa}};

    \node[font=\tiny, anchor=west, rotate=90]
    at ([yshift=-0.5mm,xshift=1mm]RFZo.center) {\Lab{vRFZ}: \qq{RFZi}};

>>>>

\begin{tikzpicture}[remember picture, overlay, shift={(5,-5)}]

@@

    \sankeyset{
      %% comment for gray outline
      draw/.style={
        draw=white,
        line width=0pt,line cap=round,line join=round,
      },
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/60,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      ice-to-water/.style={fill/.style={fill=none, left color=ice, right color=water},},
      ice-to-air/.style={fill/.style={fill=none, left color=ice, right color=air},},
      ice-to-black/.style={fill/.style={fill=none, top color=ice, bottom color=black},},
      ice-to-air-vert/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-water-vert/.style={fill/.style={fill=none, bottom color=ice, top color=water},},
      water-to-air-vert/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, left color=water, right color=air},},
      air-to-ice/.style={fill/.style={fill=none, left color=air, right color=ice},},
      red-to-ice/.style={fill/.style={fill=none, left color=red, right color=ice},},
      water-to-ice/.style={fill/.style={fill=none, left color=water, right color=ice},},
      black-to-ice/.style={fill/.style={fill=none, bottom color=ice, top color=black},},
      in-black/.style={draw/.style={draw=gray,thick=3},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\tiny,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

    \newcommand\labelleft[1]{ % valname
      \node[font=\tiny, anchor=east]
      at ([yshift=0mm,xshift=-3mm]#1.center) {\Lab{v#1}: \qq{#1}};
    }
    \newcommand\labelright[2]{ % valname
      \node[font=\tiny, anchor=west]
      at ([yshift=0mm,xshift=3mm]#1.center) {\qq{#1}: \Lab{#2}};
    }

@@

    \sankeyset{ice} % default color until otherwise specified
    \newcommand\yoff{2mm}

    \sankeynode{name=SF, quantity=\Q{vSF}}
    \sankeynode{name=DP, quantity=\Q{vDP}, at={[yshift=\yoff]SF.north}, anchor=right}
    \sankeynode{name=CD, quantity=\Q{vCD}, at={[yshift=\yoff]DP.north}, anchor=right}
    \sankeynode{name=RF, quantity=\Q{vRF}, at={[yshift=\yoff]CD.north}, anchor=right}

    \labelleft{SF}
    \labelleft{DP}
    \labelleft{CD}
    \labelleft{RF}

@@

    \sankeynode{name=f0, quantity=\Q{vSF}+\Q{vDP}+\Q{vCD}+\Q{vRF},
      at={[xshift=15mm, yshift=0mm]SF.right}, anchor=right,
      forked={\Q{vRF}/RFi, \Q{vCD}/CDi, \Q{vDP}/DPi, \Q{vSF}/SFi}}

@@

    \ifthenelse{\Q{vMG} > \Q{vML}} {
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vFRGAIN},
          at={[xshift=15mm]f0.right}, anchor=right,
          forked={\Q{vRFZ}/RFZi, \Q{vFRGAIN}/FG, \qq{f0}/f0i}}
    } {
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML}+\Q{vFRGAIN},
          at={[xshift=15mm]f0.right}, anchor=right,
          forked={\Q{vRFZ}/RFZi, \Q{vFRGAIN}/FG, \Q{vML}/MLi, \qq{f0}/f0i}}
    }

@@

    \ifthenelse{\Q{vMG} > \Q{vML}}
    {
      \sankeyfork{f1}{\Q{vRFZ}/RFZo, \Q{vSU}/SU, \Q{vRU}+\Q{vEV}/f8, \Q{vDYN}/f6,
        \Q{vGZRET}/GZ, \Q{vFRLOSS}/FL, \Q{vBM}/BM, \Q{vMG}/MG}
    }{
      \sankeyfork{f1}{
        %% \Q{vMG}/MG,
        \Q{vRFZ}/RFZo, \Q{vSU}/SU, \Q{vRU}+\Q{vEV}/f8, \Q{vDYN}/f6,
        \Q{vGZRET}/GZ, \Q{vFRLOSS}/FL, \Q{vBM}/BM}
    }

    \sankeyturnleft{RFZo}{1}
    \sankeydubins[minimum radius=5mm,ice-to-water-vert]{RFZo}{RFZi}

    \sankeyadvance{f6}{10mm}
    \sankeyfork{f6}{\Q{vICE}/CALV, \Q{vSUB}/SUB}
    \sankeyadvance[ice-to-water]{SUB}{10mm}

    \sankeynode{name=CALVa, quantity=\qq{CALV}, at={[yshift=\yoff]SUB.left}, anchor=right}
    \sankeyoutin{CALV}{CALVa}

    \sankeynode{name=f8a, quantity=\qq{f8}, at={[yshift=\yoff]CALVa.left}, anchor=right}
    \sankeyoutin[ice-to-water]{f8}{f8a}

    \sankeynode{name=GZa, quantity=\qq{GZ}, at={[yshift=-\yoff]SUB.right}, anchor=left}
    \sankeyoutin{GZ}{GZa}

    \sankeynode{name=FLa, quantity=\qq{FL}, at={[yshift=-\yoff]GZa.right}, anchor=left}
    \sankeyoutin{FL}{FLa}

    \sankeynode{name=BMa, quantity=\qq{BM}, at={[yshift=-\yoff]FLa.right}, anchor=left}
    \sankeyoutin[ice-to-water]{BM}{BMa}

    \sankeyadvance[out-red]{FLa}{10mm}
    \sankeyend[out-red]{FLa}
    \labelright{FLa}{vFRLOSS}

    \ifnum \numexpr\Q{vMG} > \Q{vML}
      \sankeynode{name=MGa, quantity=\qq{MG}, angle=-90,
        at={[xshift=5mm,yshift=-3mm]MG.right}, anchor=right}
      \node[font=\tiny, anchor=east]
      at ([yshift=0mm,xshift=0mm]MGa.right) {Mass gain: \qq{MGa}};
      \sankeyoutin{MG}{MGa}
    \fi

    \sankeyfork{f8a}{\Q{vEV}/EV, \Q{vRU}/RU}
    \sankeynode{name=EVa, quantity=\qq{EV},
      at={[yshift=2mm,xshift=5mm]f8a.left}, anchor=left, angle=45}
    \sankeyoutin[water-to-air]{EV}{EVa}
    \sankeyadvance[air]{EVa}{1mm}
    \sankeyend[air]{EVa}

    \sankeynode{name=SUa, quantity=\qq{SU},
      at={[xshift=-6mm]EVa.left}, anchor=right, angle=45}
    %% \sankeyoutin[ice-to-air{SU}{SUa}
    \sankeydubins[minimum radius=6mm,ice-to-air]{SU}{SUa}
    \sankeyend[air]{SUa}

    \ifthenelse{\Q{vMG} < \Q{vML}} { % mass loss
      \sankeynode{name=ML, quantity=\Q{vML},
        at={[yshift=6mm]RF.north}, anchor=right, angle=-45}
      \node[font=\tiny, anchor=east]
      at ([xshift=-3mm,yshift=2mm]ML.west) {Mass loss: \qq{ML}};

      % frontal advance next to drawdown (mass loss)
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[yshift=0mm,xshift=6mm]ML.left}, anchor=right, angle=-45}

      \sankeystart[red]{ML}
      \sankeyadvance[red]{ML}{5mm}
      \sankeyoutin[red-to-ice]{ML}{MLi}
    }{ % mass gain
      \sankeyadvance[ice-to-black]{MGa}{3mm}
      \sankeyend[black]{MGa}
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[xshift=-15mm,yshift=8mm]RFZi.right}, anchor=left, angle=-45}
    }

    \ifnum \numexpr\qq{FGi} > 0
    \sankeystart[in-black]{FGi}
    \sankeyoutin[in-black]{FGi}{FG}
    \node[font=\tiny, anchor=east]
    at ([xshift=-3mm,yshift=3mm]FGi.west) {Frontal advance: \qq{FGi}};
    \fi

    \sankeyadvance[ice-to-water,out-red]{GZa}{10mm}
    \sankeyend[water,out-red]{GZa}
    \sankeyadvance{CALVa}{10mm}
    \sankeyend{CALVa}

    \sankeyset{water}
    \sankeyadvance{RU}{10mm}; \sankeyend{RU}
    \sankeyadvance{BMa}{10mm}; \sankeyend{BMa}
    \sankeyadvance{SUB}{10mm}; \sankeyend{SUB}

    \labelright{RU}{vRU}
    \labelright{BMa}{vBM}
    \labelright{SUB}{vSUB}
    \labelright{CALVa}{vICE}
    \labelright{GZa}{vGZRET}

    \node[font=\tiny, anchor=west]
    at ([yshift=4mm,xshift=\yoff]SUa.west) {\qq{SUa}: \Lab{vSU}};

    \node[font=\tiny, anchor=west]
    at ([yshift=0mm,xshift=\yoff]EVa.west) {\qq{EVa}: \Lab{vEV}};

    \node[font=\tiny, anchor=east]
    at ([yshift=-0.5mm,xshift=1mm]RFZo.center) {\Lab{vRFZ}: \qq{RFZi}};
